\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-05-25 paper/paper.tex
Data Section Edits.

\section{Data}
Backblaze is a company that offers backup storage to protect against data loss.  While selling storage space is Backblaze's main business, since 2013 it has been collecting data on hard drives operating at its facility.  The purpose is to provide consumers and businesses with reliability information on different hard drive brands and models.  The hard drives continuously spin in controlled storage pods where they run until failure.  When a hard drive fails it is permanently removed, and new hard drives are regularly added to the storage pods.  In addition, the number of storage pods is increasing as Backblaze adds new hard drive brands to the sample.  Every quarter Backblaze makes its data publicly available through their website \cite{backblaze}. In addition, Backblaze publishes summary statistics of the different hard drive models currently operating.  No other analysis or modeling of the failure data is provided; however, Backblaze does encourage the public to further analyze its data, which for this paper goes through the first quarter of 2016.

As of the first quarter of 2016, Backblaze was collecting data on 63 different hard drive models.  Some drive models have been running since 2013, while others have been added at a later date.  There are a total of 75,297 hard drives running.  The distribution of drives by model varies: some models have only have a service record for a single drive; the maximum number of service records for a single drive model is 35,860.  We can also look at the distribution of total number of failures and total time on test across all drive models.  As seen below, some drive models contain a lot of information, while others have few failures or a little time in operation. [INSERT FIGURE 1]. \\

@@

In addition to graphically examining model fits via posterior credible bands, we compared the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with the $i$th data point removed.  The final expected point-wise predictive density is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).  We computed the elpd for all 4 models using the R package loo \cite{loo}.  When $n$ is large, the distribution of the elpd is approximately normal and models can be statistically compared.  We calculated the difference in expected predictive accuracy for Model 4 vs 3, Model 3 vs 2, and Model 2 vs 1, as well as the standard error of the difference (Table 1).  As the model complexity increased, the expected predictive accuracy improved.  Of all the models, Model 4 had the best predictive accuracy and was significantly better than the other 3 models.

\begin{table}[H]
\centering
\begin{tabular}{rrrrrrr}
  \hline
 & elpd\ & Diff(elpd)\ & SE(Diff) \\ 
  \hline
Model 4 & -13309.5 & 40.7 & 11.3 \\ 
Model 3 & -13350.2 & 458.8 & 31.0  \\ 
Model 2 & -13809.0 & 3674.6 & 96.2 \\ 
Model 1 & -17483.6  \\ 
   \hline
\end{tabular}
\caption{Model Comparison Based on LOO}
\label{table:1}
\end{table}

>>>>

\section{Data}
Backblaze is a company that offers backup storage to protect against data loss.  While selling storage space is Backblaze's main business, since 2013 it has been collecting data on hard drives operating at its facility.  The purpose is to provide consumers and businesses with reliability information on different hard drive brand models.  The hard drives continuously spin in controlled storage pods where they run until failure.  When a hard drive fails it is permanently removed, and new hard drives are regularly added to the storage pods.  In addition, the number of storage pods is increasing as Backblaze adds new hard drive models to the sample.  Every quarter Backblaze makes its data publicly available through their website \cite{backblaze}. In addition, Backblaze publishes summary statistics of the different hard drive models currently operating.  No other analysis or modeling of the failure data is provided; however, Backblaze does encourage the public to further analyze its data, which for this paper goes through the first quarter of 2016.

As of the first quarter of 2016, Backblaze was collecting data on 63 different hard drive models.  Some drive models have been running since 2013, while others were added at a later date.  There are a total of 75,297 hard drives in operation.  The distribution of drives by model varies: some models have only have a service record for a single drive; the maximum number of service records for a single drive model is 35,860.  We can also look at the distribution of total number of failures and total time on test across all drive brand models.  As seen in Figure \ref{fig1}, some drive models contain a lot of information, while others have few failures or little time in operation.

\begin{figure}[H]
\includegraphics[width=\textwidth]{fig/data_sum.pdf}
\caption{Left: Total number of failures (log scale) for each of the drive-models in the Backblaze data. Right: Total time in operation (log scale) for each of the drive-models in the Backblaze data.  Both plots are sorted based on the total number of failures.}
\label{fig2}
\end{figure}

@@

In addition to graphically examining model fits via posterior credible bands, we compared the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters rather than re-fitting the model with different data sets \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with the $i$th data point removed.  The final expected log point-wise predictive density (elpd) is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).  We computed the elpd for all 4 models using the R package loo \cite{loo}.  When $n$ is large, the distribution of the elpd is approximately normal and different models can be statistically compared.  We calculated the difference in expected predictive accuracy for Model 4 vs 3, Model 3 vs 2, and Model 2 vs 1, as well as the standard error of the difference (Table 1).  As the model complexity increased, the expected predictive accuracy improved.  Of all the models, Model 4 had the best predictive accuracy and was significantly better than the other 3 model specifications.

\begin{table}[H]
\centering
\begin{tabular}{rrrrrrr}
  \hline
 & ELPD \ & Difference in ELPD \ & SE of the Difference \\ 
  \hline
Model 4 & -13309.5 & 40.7 & 11.3 \\ 
Model 3 & -13350.2 & 458.8 & 31.0  \\ 
Model 2 & -13809.0 & 3674.6 & 96.2 \\ 
Model 1 & -17483.6  \\ 
   \hline
\end{tabular}
\caption{Expected Log Pointwise Predictive Density (ELPD) for each model specification.  Each model is compared to the more parsimonious model below.  The estimated difference of expected leave-one-out prediction errors between the two models, as well as the standard error of the difference, is also presented.}
\label{table:1}
\end{table}
